IRTF Spectro-Photometry of Rotating Brown Dwarfs

### 2016-11-06 ms.tex
I added a sentence about 2MASS WISE 1906.
I added a reference to Gagne et al. 2015 on 2MASS J1821.
I corrected the refrence from Banyan 5 to Banyan 7 and added the derived spectral types and effective temperatures.

We observed the three brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L5 brown dwarf known to be variable.

\begin{table*}
\begin{center}
\begin{tabular}{cccc}
Name & Rotation Period & Spectral Type & K magnitude \\
-- & hr & -- & -- \\
\hline \hline
2MASS J1821+14010 & 4.2\footnote{\citet{metchev2015weatherII}} & L4.5 - L5 & 11.14 \\
2MASS J0835-019 & 9 & L5 & 11.65 \\
\end{tabular}
\end{center}
\end{table*}

@@

We observed 2MASS J1821 and J0835 each for one night as part of a pilot program to explore a variety of brown dwarfs with different variability levels and atmospheric temperatures.
Table \ref{tab:obsParam} shows the observing parameters for each target including the integration time, number of integrations and reference star.

@@

\section{Simple Model Fits}

>>>>

We observed the three brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
The spectral type is peculiar and has also been designated as L4 \citep{gagne2015banyan7}.
2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L5 brown dwarf known to be variable.

\begin{table*}
\begin{center}
\begin{tabular}{ccccr}
Name & Rotation Period & Spectral Type & K magnitude  & T$_\mathrm{eff}$ \\
-- & (hr) & -- & -- & (K) \\
\hline \hline
2MASS J1821+14010 & 4.2\tablenotemark{a} & L4 Pec\tablenotemark{b} - L5 Pec\tablenotemark{c} & 11.14 & 1600 $\pm$ 100\tablenotemark{b} \\
2MASS J0835-019 & 9 & L4 Pec\tablenotemark{b} - L5 & 11.65 & 1800 $\pm$ 100\tablenotemark{b} \\
\end{tabular}
\end{center}
\tablenotetext{a}{\citet{metchev2015weatherII}.}
\tablenotetext{b}{\citet{gagne2015banyan7}.}
\tablenotetext{c}{\citet{looper2008peculiarLdwarfs}}

\end{table*}

@@

We observed 2MASS J1821 and J0835 each for one night as part of a pilot program to explore a variety of brown dwarfs with different variability levels and atmospheric temperatures.
The program also included WISE J1906+4011, but weather prevented successful observations of this brown dwarf.
Table \ref{tab:obsParam} shows the observing parameters for each target including the integration time, number of integrations and reference star.

@@

\section{Sinusoidal Model Fits}
